---
title: "Jackknife Sampling"
author: "Nicholas F. Brazeau"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

devtools::install_github("IDEELResearch/vcfR2plsmdmcalc")
library(vcfR2plsmdmcalc)
data("pfcross_subset", package = "vcfR2plsmdmcalc")
pfcross_subset

data("pf3k_subset", package = "vcfR2plsmdmcalc")


```

This vignette provides basic functionality for the function `block_jackknife`. Of note, this function is largely redundant with the `block_jackknife` function in the `[vcfdo](https://github.com/IDEELResearch/vcfdo)` package.  

## Quick Start
The expectation is that this function will be used to iterate through samples in a vcf. As a result, each sample is a vector. As a result, we can capitalize on vectorization with R and use the `apply` suite of functions. For example, below we calculate within-sample _He_.
  
```{r}
gtmat <- vcfR::extract.gt(pfcross_subset, element = "GT")
gtmat[gtmat == "0/0"] <- 0
gtmat[gtmat == "0/1"] <- 0.5
gtmat[gtmat == "1/1"] <- 1
gtmat <- apply(gtmat, 2, as.numeric)

HeCalc <- function(gt){
  1 - ((sum(gt == 0)/sum(!is.na(gt)))^2 + (sum(gt == 1)/sum(!is.na(gt)))^2)
}

He <- apply(gtmat, 2, block_jackknife, statistic = HeCalc, block_size = 6)

```


## Running Jackknife under the `THEREALMcCOIL` Model 
This function makes use of the `McCOILR` package by [OJ Watson]() which is a wrapper for the Hsiao-Han Chang's `THEREALMcCOIL` package (PMC5300274). However, given this structure, we cannot use the `block_jackknife` structure above which expects _numeric_ or _integer_ vectors as the input. Instead, we pass a dataset that is ready for a `THEREALMcCOIL` analysis (see [here](https://github.com/Greenhouse-Lab/THEREALMcCOIL) for file structure) and perform jackknife re-sampling on the loci. In each jackknife-replication, a specific value of MOI is drawn from the posterior distribution of the `THEREALMcCOIL` MCMC sampling phase output.    
**Below we explore this function.**

### A single iteration
```{r}

gtmat <- vcfR::extract.gt(pf3k_subset, element = "GT")
gtmat <- gtmat[1:100,1:40]
gtmat[is.na(gtmat)] <- -1
gtmat[gtmat == "0/0"] <- 0
gtmat[gtmat == "0/1"] <- 0.5
gtmat[gtmat == "1/1"] <- 1
gtmat <- t( apply(gtmat, 2, as.numeric) )
rownames(gtmat) <- colnames(pf3k_subset@gt)[2:41]
colnames(gtmat) <- paste0(pf3k_subset@fix[,1], "_", vcf@fix[,2])[1:100]


ret <- sample_posterior_mccoilr_categorical(gtmat, 
                                            path = paste0(getwd(), "/scratch/mccoiltests/"),
                                            output="output_catMOI.txt",
                                            maxCOI=25, threshold_ind=20, threshold_site=20,
                                            totalrun=1000, burnin=100, M0=15, 
                                            e1=0.05, e2=0.05,
                                            err_method=1)

ret %>% 
  DT::datatable(., extensions='Buttons',
                options = list(
                searching = T,
                pageLength = 5,
                dom = 'Bfrtip', 
                buttons = c('csv')))
```

### Jackknife Resampling 
Issues are the mccoilr_categorical function writes out. If you want to keep all of the raw data (and not overwrite it) need to loop through the different potential output files. otherwise can overwrite it but will be left with the final jackknife iteration 

**directory must be empty**
**took output over from user... annoying but should fix**
```{r}

ret <- block_jackknife4sample_posterior_mccoilr_categorical( 
        data = gtmat, 
        path = path, 
        block_size = 1,
        maxCOI=25, threshold_ind=20, threshold_site=20,
        totalrun=1000, burnin=100, M0=15, 
        e1=0.05, e2=0.05,
        err_method=1)





```

